oREVIRT analysis

### 2022-11-08 analysis/irt_analysis.Rmd
rasch plus geuss selected

@@

```{r}
rel_dat <- irt_dat%>%
  select(-sex, -order, -aoa_german_comb)%>%
  filter(targetWord %in% rasch_selected_items)%>%
  group_by(subjID)%>%
  distinct(targetWord, .keep_all = T)%>%
  pivot_wider(names_from = targetWord, values_from = correct)%>%
  ungroup()%>%
  select(-subjID)

>>>>

brms::bayes_R2(irt1_guess)
```

@@

```{r}
rel_dat <- irt_dat%>%
  select(-sex, -order)%>%
  filter(targetWord %in% sel_items_rasch)%>%
  group_by(subjID)%>%
  distinct(targetWord, .keep_all = T)%>%
  pivot_wider(names_from = targetWord, values_from = correct)%>%
  ungroup()%>%
  select(-subjID)
